\chapter*{Abstract}

\addcontentsline{toc}{chapter}{Abstract}
Natural Language Processing encompasses a set of tasks that are aimed at analyzing natural language data, allowing computer systems to somehow understand the content of a document in order to make inferences from it. Automated determination of a person's characteristics such as gender, political leanings, age and other demographic and psychological aspects are examples of natural language processing; specifically, they belong to the group of author profiling tasks.
\\
This paper proposes a solution for Twitter users profiling tasks based on Artificial Intelligence and with a multilingual approach. The developed model employs Deep Learning techniques, which have been studied by other authors. However, this paper introduces a modular treatment to author profiling and the use of Graph-Based Neural Networks to model the relationships between the elements that compose a user profile. In addition, a comparative study with other architectures such as Long-Short Term Memory Networks is carried out and a modification of the Impostor Method originally used for the Authorship Verification task is introduced, so that it is able to deal with DL-based representations to classify the profile.
\\
To perform the profiling following a modular strategy: i) the profile elements i.e., tweets, are modeled through Transformers neural models or Convolutional Networks at word and character levels; ii) the encodings of the tweets of a profile are interpreted as a sequence or as nodes within a graph, which are processed with a LSTM or a Convolutional Network in Graphs respectively, to model and classify the profile.\\ Experimental results show that the proposed model achieves significant performance within the state of the art in the evaluated tasks.
\\


\textbf{Key words:} Author Profiling, Deep Learning, Transformers, Convolutional Networks in Graphs.
